Automated Synthesis of State-Space Digital Controllers

### 2016-11-21 cav2017/cav2017.tex
add comments to Cristina

\begin{figure}
\centering
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1.5cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=7cm,
	minimum height=.8cm,
	label={\sc Validation oracles},] (verif) {};
   \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
   \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.9cm]verif.center) {{\sc validate general}};
   } 
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \& \\
   \node (gp) {Program Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
   \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
   }   
    \\
  };

@@

with $\vec{w} \sim \mathcal{N}(0,Q)$\\
Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
which may restricts the observability of the statespace from the output space.
\begin{equation}
\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t)
\end{equation}

Discretization of an continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
for the input $\vec{u}$ and continuous integration for the noise $\vec{w}$, to
\begin{align}
\label{eq:discretization}
\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d\vec{u}_k + \vec{w}_k\\
y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k 
\end{align}
with covariance for $\vec{w}_k \sim \mathcal{N}(0,Q_d)$
where
\begin{align}
\label{eq:discretize}
\vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s}\\
\vec{B}_d &= \int_{0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B}\\
\vec{C}_d &= \vec{C}\\
\vec{D}_d &= \vec{D} \\
Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt
\end{align}
and $T_s$ is the sample time. Then
\begin{align*}
x(kT)=x_k \wedge y(kT) = y_k, \forall k
\end{align*}
Let $g_d(k)=\mathcal{G}(t,g(t),T)$ be a function that performs the discretization described above, where $g(t)$
represents the continuous dynamics and $g_d(k)$ the corresponding discrete dynamics. 
Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_d(k))$ be the corresponding Laplace and Z-transforms
of $g(t)$ and $g_d(k)$. Given this relation, we have 
$$G_d(z)=G(z)|_{z=e^{sT}} : g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s}$$
Where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
which could cause 'phantom poles' to appear otherwise. 
The eigenvalues of $\vec{A}_d$ corresponding to the poles of $G_d(z)$, and those of $\vec{A}$ corresponding to the poles of $G(s)$ are similarly related.
$\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in \sigma(\vec{A}_d) \wedge \lambda_i \in \sigma(\vec{A})$
where $\sigma(\cdot)$ is the spectrum of a matrix.
The following remark is worth mentioning regarding the above.
\begin{remark}
The witnessed maximum amplitude of the discrete signals $x_k,y_k$ may be smaller to that of $x(t),y(t)$ due to synchronism at fraction-frequency sampling.
This means that reasoning about the statespace must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
\end{remark}
Since \eqref{eq:discretization} is a bisimulation of \eqref{eq:dynamical}, we may use the semantics in section \ref{sec:model_semantics} 
to model continuous dynamical systems.

>>>>

\textcolor{red}{LC: Cristina, may I ask you to expand further this section by connecting it to our control-synthesis work?}
\begin{figure}
\centering
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1.5cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=7cm,
	minimum height=.8cm,
	label={\sc Validation oracles},] (verif) {};
   \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
   \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.9cm]verif.center) {{\sc validate general}};
   } 
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \& \\
   \node (gp) {Program Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
   \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
   }   
    \\
  };

@@

\noindent with $\vec{w} \sim \mathcal{N}(0,Q)$.\\
Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
which may restricts the observability of the state-space from the output space.
\begin{equation}
\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t)
\end{equation}

Discretization of an continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
for the input $\vec{u}$ and continuous integration for the noise $\vec{w}$, to
\begin{align}
\label{eq:discretization}
\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d\vec{u}_k + \vec{w}_k\\
y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k 
\end{align}
with covariance for $\vec{w}_k \sim \mathcal{N}(0,Q_d)$
where
\begin{align}
\label{eq:discretize}
\vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s}\\
\vec{B}_d &= \int_{0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B}\\
\vec{C}_d &= \vec{C}\\
\vec{D}_d &= \vec{D} \\
Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt
\end{align}
and $T_s$ is the sample time. Then
\begin{align*}
x(kT)=x_k \wedge y(kT) = y_k, \forall k
\end{align*}
Let $g_d(k)=\mathcal{G}(t,g(t),T)$ be a function that performs the discretization described above, where $g(t)$
represents the continuous dynamics and $g_d(k)$ the corresponding discrete dynamics. 
Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_d(k))$ be the corresponding Laplace and Z-transforms
of $g(t)$ and $g_d(k)$. Given this relation, we have 
$$G_d(z)=G(z)|_{z=e^{sT}} : g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s}$$
Where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
which could cause 'phantom poles' to appear otherwise. 
The eigenvalues of $\vec{A}_d$ corresponding to the poles of $G_d(z)$, and those of $\vec{A}$ corresponding to the poles of $G(s)$ are similarly related.
$\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in \sigma(\vec{A}_d) \wedge \lambda_i \in \sigma(\vec{A})$
where $\sigma(\cdot)$ is the spectrum of a matrix.
The following remark is worth mentioning regarding the above.
\begin{remark}
The witnessed maximum amplitude of the discrete signals $x_k,y_k$ may be smaller to that of $x(t),y(t)$ due to synchronism at fraction-frequency sampling.
This means that reasoning about the state-space must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
\end{remark}
Since \eqref{eq:discretization} is a bisimulation of \eqref{eq:dynamical}, we may use the semantics in section \ref{sec:model_semantics} 
to model continuous dynamical systems.
